%% Latex I've cobbled together from the far corners of the world. Feel free to copy and paste, fork, clone, or anything you like.

\input{main.tex}

\input{include/header.tex}
\textcolor{my-grey}{\dotfill}
\bigbreak


23 July 2019\\
\bigbreak

Oregon State University\\
Corvallis, OR

\bigbreak

To Whom it May Concern,

\bigbreak

I admire the track record that Oregon State University has in regards to setting high standards for quality security and network solutions for users. I believe that the Application Software Developer position can work towards such a mission.

\bigbreak

\textbf{EXPERIENCE.} I am an exemplary candidate for your \textbf{Application Software Developer} position as I take the importance of providing responsive and quality software to heart. In my scholastic career, I have spearheaded numerous projects that deliver upon these goals, including:

\begin{itemize}[label=$\triangleright$]
    \myItem{\textcolor{my-blue}{\href{https://voyager-index.herokuapp.com/}{Voyager Index}}}a quality of life application to help world travelers find their next home.
    \myItem{\textcolor{my-blue}{\href{https://github.com/RemoveMyWaste/}{RemoveMyWaste}}}an application that helps users dispose of hazardous materials.
    \myItem{\textcolor{my-blue}{\href{https://github.com/lbeckman314/convida/}{Convida}}}Conway's Game of Life powered by WebAssembly.
\end{itemize}

\bigbreak

\textbf{WORK SKILLS.} Through a combination of courses and extracurricular pursuits, I have a solid experience with major software development foundations. My abilities in planing, executing, and maintaining web, mobile, and database projects using a wide range of languages and frameworks can greatly serve your business pursuits.

\bigbreak

The above experiences and my attached resume provide an overview of my qualifications for this position. Following a review of my accomplishments, I would greatly appreciate the opportunity to discuss an Application Software Developer position at Oregon State University.

\bigbreak

Sincerely,\\

Liam Beckman

\vfill

\textcolor{my-grey}{\dotfill}
\medbreak

\input{include/footer-coverletter.tex}
\end{document}
