\showoff
{Ski and Snowboard Technician and Shop Hand}
{Mountain Sports}
{Welches, OR}
{Winter 2018, Winter 2019}
\begin{itemize}[label=$\triangleright$]
    \item Assisted customers in tuning skis and snowboards, recommending local trails and recreational areas, and renting and buying select winter gear. Other responsibilities included itemizing, inspecting, and restocking equipment.
\end{itemize}

\myBreak

\showoff
{Lab Prep Assistant}
{University of Oregon Honors Biology Lab}
{Eugene, OR}
{2014 --- 2015}
\begin{itemize}[label=$\triangleright$]
    \item Prepped materials and cleaned up workstations for undergraduate biology lab courses.
    \item Set up student computers with programs used to collect, analyze, and present lab data.
    \item Monitored growth and maintenance of plant, animal, and microbial lab specimens.
\end{itemize}

\myBreak

\showoff
{Student Researcher --- Botanical Genetics}
{University of Minnesota}
{Minneapolis, MN}
{Summer 2014}
\begin{itemize}[label=$\triangleright$]
    \item Conducted research involving botanical DNA isolation, purification, sequencing, and analysis.
    \item Presented results and conclusions at three scientific conferences.
\end{itemize}

\myBreak

\showoff
{Student Researcher --- Ecology and Restoration}
{H.J. Andrews Experimental Forest}
{Blue River, OR}
{Summer 2013}
\begin{itemize}[label=$\triangleright$]
    \item Analyzed forest networks and plant response to fire disturbances.
    \item Surveyed plant communities in experimental sub-alpine meadows as part of ongoing research.
    \item Published study in \textit{Restoration Ecology: The Journal of the Society for Ecological Restoration} ("Vegetation Recovery in Slash-Pile Scars Following Conifer Removal in a Grassland-Restoration Experiment", November 2014).
\end{itemize}

